---
title: "High resolution monitoring of antimicrobial consumption in Vietnamese small-scale chicken farms highlights discrepancies between study metrics"
output:
  html_document:
    theme: cosmo
    toc: true
editor_options: 
  chunk_output_type: console
---

```{r general_options, include = FALSE}
knitr::knit_hooks$set(
  margin = function(before, options, envir) {
    if (before) par(mgp = c(1.5, .5, 0), bty = "n", plt = c(.105, .97, .13, .97))
    else NULL
  },
  prompt = function(before, options, envir) {
    options(prompt = if (options$engine %in% c("sh", "bash")) "$ " else "> ")
  })

knitr::opts_chunk$set(margin = TRUE, prompt = TRUE, comment = "",
                      collapse = TRUE, cache = FALSE, autodep = TRUE,
                      dev.args = list(pointsize = 11), fig.height = 3.5,
                      fig.width = 4.24725, fig.retina = 2, fig.align = "center")

options(width = 137)
```

Here we show how to generate the
[ESVAC](https://www.ema.europa.eu/en/veterinary-regulatory/overview/antimicrobial-resistance/european-surveillance-veterinary-antimicrobial-consumption-esvac) data on the mg-to-IU and IU-to-mg
conversions as well as on the relationship between weight and age.

## Packages

Installing the required packages:

```{r}
required <- c("dplyr", "magrittr", "readxl", "tidyr")
to_install <- setdiff(required, row.names(installed.packages()))
if (length(to_install)) install.packages(to_install)
```

Loading `magrittr`:

```{r}
library(magrittr)
```

## ESVAC IU to mg conversion data

The [ESVAC](https://www.ema.europa.eu/en/veterinary-regulatory/overview/antimicrobial-resistance/european-surveillance-veterinary-antimicrobial-consumption-esvac) conversion factors are available from the table 2
of page 62 of the [OIE](http://www.oie.int) [report](http://www.oie.int/fileadmin/Home/fr/Our_scientific_expertise/docs/pdf/AMR/Survey_on_monitoring_antimicrobial_agents_Dec2016.pdf). A copy-paste of this table without headers is available
[here](https://raw.githubusercontent.com/viparc/amu_metrics/master/raw_data/esvac.txt).
We can read this file and format it to compute the following IU-to-mg convertion
vector:

```{r}
tmp <- tempfile()
download.file("https://raw.githubusercontent.com/viparc/amu_metrics/master/raw_data/esvac.txt", tmp)
```

Reading the raw data, putting in shape and writting to CSV file:

```{r}
if (!dir.exists("data")) dir.create("data")
tmp %>% 
  readLines() %>% 
  sub("^#.*", "", .) %>% 
  sub(" *", "", .) %>% 
  {.[. != ""]} %>% 
  matrix(ncol = 4, byrow = TRUE) %>% 
  as.data.frame(stringsAsFactors = FALSE) %>% 
  setNames(c("ab_vet_med", "ab_oie", "IU.mg", "mg.IU")) %>% 
  write.csv("data/esvac.csv", quote = FALSE, row.names = FALSE)
```

## Age-weight relationship

Data on chicken weights as a function of age were collected for a previous
study. The data are
[here](https://www.dropbox.com/s/5mmw31s2txbmgnx/Supplementary_Data_Frontiers.xlsx?dl=0):

```{r}
age_weight_data <- "https://www.dropbox.com/s/5mmw31s2txbmgnx/Supplementary_Data_Frontiers.xlsx?dl=0"
tmp <- tempfile(fileext = ".xlsx")
download.file(sub("dl=0", "raw=1", age_weight_data), tmp)
```

```{r}
if (!dir.exists("data")) dir.create("data")
tmp %>% 
  readxl::read_excel() %>% 
  tidyr::gather("week", "weight.kg", -FlockID, -Chicken) %>% 
  na.exclude() %>% 
  dplyr::mutate(week = sub("Week ", "", week)) %>% 
  dplyr::mutate_at(c("FlockID", "Chicken", "week"), as.integer) %>% 
  write.csv("data/age_weight.csv", quote = FALSE, row.names = FALSE)
```



